Team size and composition in home health care

### 2023-10-19 paper-presentation/paper-presentation.qmd
Layouts

The number of care workers present [$\tilde{M}$]{style="color: red;"} then follows a Binomial( $M$, $p$ ) distribution. Consequently, the properties of the effective capacity [$P$]{style="color: red;"} $= \frac{\tilde{M}}{M}$ follow directly from this observation.

@@

# generates image of productivity cdf vs total scheduled workers
# targets(list): all (cdf) values to be evaluated: i.e. all x's to Pr(P <= x)
# p: probability a worker is present on scheduled moment
# max_M: upper limit of x-axis (maximum scheduled workers)
# min_M: lower limit of x-axis (minimum scheduled workers) 
def plot_productivity(targets,p,min_M,max_M,pinned_size):
    fig, ax = plt.subplots(figsize=(9.6,7.2))
    M = np.arange(min_M, max_M)

@@

    # Draw the graph
    pos = nx.spring_layout(G)  # positions for all nodes
    nx.draw_networkx_nodes(G, pos, node_size=700)
    nx.draw_networkx_edges(G, pos, width=1.0, alpha=0.5)
    nx.draw_networkx_labels(G, pos, font_size=20)

@@

    # Draw the graph
    pos = nx.spring_layout(G)
    nx.draw_networkx_nodes(G, pos)
    nx.draw_networkx_edges(G, pos)
    nx.draw_networkx_labels(G, pos)

>>>>

The number of care workers present [$\tilde{M}$]{style="color: red;"} then follows a Binomial($M$, $p$) distribution. Consequently, the properties of the effective capacity

[$P$]{style="color: red;"} $= \frac{\tilde{M}}{M}$

follow directly from this observation.

@@

# generates image of productivity cdf vs total scheduled workers
# targets(list): all (cdf) values to be evaluated: i.e. all x's to Pr(P <= x)
# p: probability a worker is present on scheduled moment
# max_M: upper limit of x-axis (maximum scheduled workers)
# min_M: lower limit of x-axis (minimum scheduled workers) 
def plot_productivity(targets,p,min_M,max_M,pinned_size):
    fig, ax = plt.subplots(figsize=(12,5))
    M = np.arange(min_M, max_M)

@@

    # Draw the graph
    pos = nx.spring_layout(G)  # positions for all nodes
    nx.draw_networkx_nodes(G, pos, node_size=700, node_color="tomato")
    nx.draw_networkx_edges(G, pos, width=1.0, alpha=0.5)
    nx.draw_networkx_labels(G, pos, font_size=20, font_color="white")

@@

    # Draw the graph
    pos = nx.spring_layout(G)
    nx.draw_networkx_nodes(G, pos, node_color="tomato")
    nx.draw_networkx_edges(G, pos)
    nx.draw_networkx_labels(G, pos, font_color="white")
